\begin{cccFunctionality}
    {\wrapper{\funcGRO}}
    {random-oracle-wrapper}
    {The random oracle wrapper.}

    This functionality maintains state variables as follows.

    \addtocounter{table}{-1}
    \begin{tabularx}{.9\textwidth}{c  X}
        \toprule[.3mm]
        \textbf{State Variable}
         & \textbf{Description}
        \\ \midrule[.3mm]
        $\partyset \gets \emptyset$
         & The set of registered parties; the current set of corrupted parties is denoted by $\partyset'$.
        \\ \midrule
        $\tau \gets 0$
         & The (real-time) clock tick counter.
        \\ \midrule
        $h_\tau$
         & An upper bound which restricts the \func-evaluations of all alert parties at time $\tau$.
        \\ \midrule
        $q_\honestPartySet, q_\adv \gets 0$
         & The alert/adversary evaluation counter.
        \\ \bottomrule[.3mm]
    \end{tabularx}

    \paragraph{Relaying inputs to the random oracle:}
    %
    \begin{cccItemize}[nosep]
        \item Upon receiving $(\textsc{eval}, \sid, x)$ from \adv on behalf of a corrupted party $P \in \partyset'$ or a de-synchronized party \party, first execute \textit{Round Reset}, then do the following.
        %
        \begin{cccEnum}[nosep]
            \item Set $q_\adv \gets q_\adv + 1$.
            \item \textbf{If} $q_\adv \le h_\tau$ \textbf{then} forward the request to \funcGRO and return to \adv whatever \funcGRO returns.
        \end{cccEnum}

        \item Upon receiving $(\textsc{eval}, \sid, x)$ from an alert party \party, first execute \textit{Round Reset}, then do the following.
        %
        \begin{cccEnum}[nosep]
            \item Set $q_\honestPartySet \gets q_\honestPartySet + 1$.
            \item \textbf{If} $q_\honestPartySet \le h_\tau$ \textbf{then} forward the request to \funcGRO and return to \party whatever \funcGRO returns.
            \item \textbf{If} $q_\honestPartySet \ge h_\tau$ \textbf{then} send $(\textsc{clock-update}, \sid_C)$ to \funcClock.
        \end{cccEnum}
    \end{cccItemize}

    \paragraph{Corruption handling:}
    %
    \begin{cccItemize}[nosep]
        \item Upon receiving $(\textsc{corrupt}, \sid, \party)$ from the adversary, set $\partyset' \gets \partyset' \cup \party$.
    \end{cccItemize}

    \medskip\emph{Procedure Round-Reset:}
    %
    Send $(\textsc{clock-read}, \sid_C)$ to \funcClock and receive $(\textsc{clock-read}, \allowbreak \sid_C, \tau')$ from \funcClock. If $|\tau - \tau' | > 0$, then set $q_\honestPartySet, q_\adv \gets 0$ and $\tau \gets \tau'$.
\end{cccFunctionality}
